|

### 2023-01-24 paper_comparison/paper_comparison/paper_comparison.Rmd
update color pal for the last section of the result

```{r poly-power-j, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. "}

poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>%
  select(shape, log_effect_size, reject, conv_or_not) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = shape), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "Vivid")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Non-linearity shape")
```

@@

  # Draw bootstrap for Left-triangle
  geom_ribbon(data = ~get_boot_conf(filter(.x, 
                                           conv_or_not == "Visual", 
                                           a == "Left-triangle"),
                                    log_effect_size,
                                    reject,
                                    times = 1000) %>%
                mutate(conv_or_not = "Visual"),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rev(rcartocolor::carto_pal(3, "Vivid"))[3],
              alpha = 0.2) +

  # Draw bootstrap for Right-triangle
  geom_ribbon(data = ~get_boot_conf(filter(.x, 
                                           conv_or_not == "Visual", 
                                           a == "Right-triangle"),
                                    log_effect_size,
                                    reject,
                                    times = 1000) %>%
                mutate(conv_or_not = "Visual"),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rev(rcartocolor::carto_pal(3, "Vivid"))[2],
              alpha = 0.2) +

  # Theme
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Vivid")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```

@@

>>>>

```{r poly-power-j, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. Power curves with higher order of non-linearity are drawn with deeper colours."}

poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>%
  select(shape, log_effect_size, reject, conv_or_not) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = shape), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "TealGrn")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Non-linearity shape")
```

@@

  # Draw bootstrap for Left-triangle
  geom_ribbon(data = ~get_boot_conf(filter(.x, 
                                           conv_or_not == "Visual", 
                                           a == "Left-triangle"),
                                    log_effect_size,
                                    reject,
                                    times = 1000) %>%
                mutate(conv_or_not = "Visual"),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rcartocolor::carto_pal(3, "Earth")[1],
              alpha = 0.2) +

  # Draw bootstrap for Right-triangle
  geom_ribbon(data = ~get_boot_conf(filter(.x, 
                                           conv_or_not == "Visual", 
                                           a == "Right-triangle"),
                                    log_effect_size,
                                    reject,
                                    times = 1000) %>%
                mutate(conv_or_not = "Visual"),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rcartocolor::carto_pal(3, "Earth")[3],
              alpha = 0.2) +

  # Theme
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Earth")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```

@@

1. summarise paper content
2. briefly describe what was learned
3. how does this apply more broadly than simple regression
4. where does this lead? Computer vision residual plot reading

# Acknowledgement

1. software tools
2. point to github repo (create a new one)
3. summarise the supplementary material
